Measuring Political Freedom Around the World

### 2020-11-10 slides.Rmd
outline of slideshow

# Introduction
- study political freedom as a function of social, economic, political factors
- gapminder data
- filtered to only include OECD

@@

# Define political freedom
summarsze fh index

@@

---
# Model

@@

\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}

---
# show charts

@@

# Some model test

```{r}
broom::tidy(model_df5) %>% 
  kableExtra::kable()
```
---

```{r}
broom::tidy(model_df5) %>% 
  kableExtra::kable() %>% 
  kableExtra::row_spec(4, bold = T, color = "white", background = "#D7261E")
```

>>>>

# Outline

* What factors are associated with an increase in political freedom?

--

* study political freedom as a function of social, economic, political factors

--

* From Data provided by the Gapminder Foundation.

---
class: inverse, middle, center

# Data

@@

# Data

* filtered to only include OECD Countries from year 2000 to 2018

# Define political freedom

--

* Freedomhouse index

--

* summarsze fh index

@@

class: inverse, middle, center

# Model
---

class: center, middle

@@

$$
\large
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$

---
class: center

$$
\tiny
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$

```{r}
broom::tidy(model_df5) %>% 
  kableExtra::kable()
```
---
class: center
$$
\tiny
\begin{align}
\operatorname{polrights} = \beta_{0} + \beta_{1}(\operatorname{corruption\_perception\_index\_cpi}) +\\ \beta_{2}(\operatorname{edu\_exp\_gdp\_per\_person}) +\\ \beta_{3}(\operatorname{life\_expectancy\_years}) +\\ \beta_{4}(\operatorname{military\_spending\_pct\_of\_gdp}) +\\ \beta_{5}(\operatorname{murder\_per\_mil\_people}) + \epsilon
\end{align}
$$
```{r}
broom::tidy(model_df5) %>% 
  kableExtra::kable() %>% 
  kableExtra::row_spec(4, bold = T, color = "white", background = "#D7261E")
```

@@

class: center, middle

# Thanks You and We are Happy to Take Questions

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).
